---
title: "functions"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{functions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## function1

a Rayleigh sampler with acceptance-rejection method using R. The Rayleigh density is
$$
f(x)=\frac{x}{\sigma^{2}} e^{-x^{2} /\left(2 \sigma^{2}\right)}, \quad x \geq 0, \sigma>0
$$
Let g(x) be the chisquare(4) density, we can easily get c = $\frac{4}{\sigma^{2}} e^{\sigma^{2}/8}$.
On average, $cn$ iterations will be required for a sample size $n$.

```{r}
library(Rcpp)
library(StatComp20073)
```


```{r eval=FALSE}
RayleighR <- function(n, sigma){
  k <- 0 
  j <- 0 
  result <- list()
  y <- numeric(n)
  while (k < n) {
    u <- runif(1)
    j <- j + 1
    x <- rchisq(1,4) 
    if (exp(-x^2/(2*sigma^2)+x/2-sigma^2/8) > u) {
      k <- k + 1
      y[k] <- x
    }
  }
  result$rd <- y
  result$it <- j
  result
}
```

for example, if we want to generate a Rayleigh(sigma = 2) random number of size $n=1000$, we need to iterate nearly 1649 times:

```{r}
n <- 1000
sigma <- 2
set.seed(345)
y <- RayleighR(n, sigma)
print(y$it)
```

## function2

a Rayleigh sampler with acceptance-rejection method using Rcpp.

```{r eval=FALSE}
#include <Rcpp.h>
using namespace Rcpp;
// [[Rcpp::export]]
NumericVector RayleighC(int n, double sigma) {
  NumericVector y(n);
  int k = 0,j = 0;
  double u=0, x=0;
  while (k < n) {
    u = runif(1)[0];
    j = j + 1;
    x = rchisq(1,4)[0];
    if (exp(-pow(x,2)/(2*pow(sigma,2))+x/2-pow(sigma,2)/8) > u) {
      k++;
      y[k] = x;
    }
  }
  return y;
}
```

```{r}
RR <- RayleighR(n,sigma)$rd
RC <- RayleighC(n,sigma)
qqplot(RR,RC)
abline(a=0,b=1,col='black')
```






